---
title: DLA/DoD 1033 Analysis
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[LO,RE]{Aspen Partition and Image Data}
- \fancyfoot[CE,CO]{\thepage}
- \fancyfoot[LE,RO]{Extreme Networks Confidential}
---

```{r echo=FALSE, results="asis"}
# Bring in all the good stuffs
source("analyze.R")
```

```{r echo=FALSE, results="asis", cache=TRUE}
# Long process here, cache it
df1033   <- give1033Data()
triangle <- selectOutTriangle(df1033)
```

# Data Sources

The [DLA’s](http://www.dispositionservices.dla.mil/) Law Enforcement Support Office (LESO) transfers excess Department of Defense
property to federal, state, and local law enforcement agencies within the United States and its Territories

Details of transfers since 1950 have been documented on this webpage.

* [http://www.dispositionservices.dla.mil/EFOIA-Privacy/Pages/ereadingroom.aspx#1033](http://www.dispositionservices.dla.mil/EFOIA-Privacy/Pages/ereadingroom.aspx#1033)

The following files available above are used in this analysis:

|File Name                |Description                   |URL                                                                    |
|-------------------------|------------------------------|-----------------------------------------------------------------------|
|tacticalatLEAAL-LA.xls|DLA/DoD 1033 Alaska - Louisiana|http://www.dispositionservices.dla.mil/EFOIA-Privacy/Documents/tacticalatLEAAL-LA.xls|
|tacticalatLEAMA-WYandTerr.xls|DLA/DoD 1033 Massachusetts - Wyoming and territories|http://www.dispositionservices.dla.mil/EFOIA-Privacy/Documents/tacticalatLEAMA-WYandTerr.xls|

# Data Transformations

All data transformations can be inspected on this project's [GitHub](http://www.github.com) project page - [https://github.com/danielschudel/TenThirtyThree/](https://github.com/danielschudel/TenThirtyThree/). The two files ```analyze.R``` and ```encodeCounties.R``` are of particular interest.

# NC

## Triangle Counties

Agencies within the following counties are included:

* Chatham
* Durham
* Orange
* Wake

### Data Summaries

```{r echo=FALSE, results="asis", fig.width=24, fig.height=12, fig.cap=""}
library(xtable)
t <- ddply(triangle, .(agencyName, shipYear, itemName), summarize, totalItems=sum(one), totalValue=sum(acquisitionValue))
t$totalValue <- dollar(as.numeric(as.character(t$totalValue)))
t <- xtable(t)
digits(t) <- 0
align(t) <- "|r|r|l|l|l|r|"
print(t, type="html", include.rownames=FALSE, floating=FALSE)
```

#### Specific Notes

* 2003 transfer of combat/assault/tactical vehicle to the Orange County Sheriff is coded as having an acquisition value of $0.01 (US Dollars).
    * This is assumed to be a clerical mistake. Five other counties received similar items with a significantly higher recorded value. The mean of those values
      is substituted for the recorded $0.01.
    * It is possible that the transferred item did have a near zero value.

### Total Value of Items Transferred

```{r echo=FALSE, results="asis", fig.width=24, fig.height=12, fig.cap=""}
plotValueByTriangleCounties(triangle)
```

### Itemization of Items Transferred

```{r echo=FALSE, results="asis", fig.width=24, fig.height=12, fig.cap=""}
plotItemsByTriangleCounties(triangle)
```

# Copying

This work is licensed under a Creative Commons Attribution-ShareAlike 4.0 International License.

Follow these links for licensing and re-use details:

* [http://creativecommons.org/licenses/by-sa/4.0/](http://creativecommons.org/licenses/by-sa/4.0/)
* [http://creativecommons.org/licenses/by-sa/4.0/legalcode](http://creativecommons.org/licenses/by-sa/4.0/legalcode)

# Adapting

This work is available on [GitHub](http://github.com) at the following URL:

* [https://github.com/danielschudel/TenThirtyThree/](https://github.com/danielschudel/TenThirtyThree/)
